---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missCforest

`missCforest` is an Ensemble Conditional Trees algorithm for Missing Data Imputation. It performs single imputation based on the [`Cforest` algorithm](https://bmcbioinformatics.biomedcentral.com/articles/10.1186/1471-2105-8-25) which is an ensemble of [Conditional Inference Trees](https://jmlr.org/papers/v16/hothorn15a.html). 

The aim of `missCforest` is to produce a complete dataset using an iterative prediction approach by predicting missing values after learning from the complete cases.

## Installing

You can install the development version of `missCforest` as follow:

``` r
#install.packages("devtools")
devtools::install_github("ielbadisy/missCforest")
```

## Examples

```{r}
library(missCforest)

# import the GBSG2 dataset
library(TH.data)
data("GBSG2")

# consider the cens variable as a factor
GBSG2$cens <- as.factor(GBSG2$cens)

# introduce randomly 30% of NA to variables
datNA <- missForest::prodNA(GBSG2, 0.2)
head(datNA)
```


You can impute all the missing values using all the possible combinations of the imputation model formula:

```{r}
impdat <- missCforest(datNA, .~., 
                      ntree = 300L,
                      minsplit = 20L,
                      minbucket = 7L,
                      alpha = 0.05,
                      cores = 4)  
head(impdat)
```

## Citing

To cite `missCforest` in publications please use:

> El Badisy I (2023). _missCforest: Ensemble Conditional Trees for Missing
  Data Imputation_. R package version 0.0.8,
  <https://CRAN.R-project.org/package=missCforest>.

A BibTeX entry for LaTeX users is

```bibtex

  @Manual{,
    title = {missCforest: Ensemble Conditional Trees for Missing Data Imputation},
    author = {Imad {El Badisy}},
    year = {2023},
    note = {R package version 0.0.8},
    url = {https://CRAN.R-project.org/package=missCforest},
  }

```

## Contributing

- If you encounter any bugs or have an idea for contribution, please [submit an issue](https://github.com/ielbadisy/missCforest/issues).

- Please include a [reprex](https://reprex.tidyverse.org/articles/articles/learn-reprex.html) for reproducibility. 
