---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missCforest

`missCforest` is an Ensemble Conditional Trees algorithm for Missing Data Imputation. It performs single imputation based on the `Cforest` algorithm.

The goal of `missCforest` is to produce a complete dataset using an iterative prediction approach by predicting missing values by learning from the complete cases.

## Installation

You can install the development version of `missCforest` as follow:

``` r
#install.packages("devtools")
devtools::install_github("ielbadisy/missCforest")
```

## Examples

```{r}
library(missCforest)
# import the iris dataset 
data(iris)

# introduce randomly 30% of NA to variables
irisNA <- generateNA(iris, 0.3)
summary(irisNA)
```


You can impute all the missing values using all the possible combinations of the imputation model formula:

```{r}
irisImp <- missCforest(irisNA, .~.)  
summary(irisImp)
```

